### 2015-10-28 weeklyReport/approach.tex
10-27 IR clustering

\section{Approach}

Our approach helps identify and integrate reusable examples in two phases:

\subsection{Example Collection Phase.}  
We identify the main features from multiple partial programs derived from informal resources. Without confined to an established code corpus, we leverage web search engine to obtain a list of code examples in the form of partial programs and use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.

\noindent{\textbf{Query Code Search Engine.}}  We use code search engine SearchCode~\cite{SearchCode} to extract code examples based on free-form queries from users.  We choose it because 1) it has good support for free-form queries,  2) it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, 3) it has complete API documentations and returns.

\noindent{\textbf{Locate Queried Features.}}  Considering that source code examples always contain multiple features, we identify program elements that are related to the queried features. I use the mean of TF-IDF weight  for each query term as a weighting factor and select all methods whose weighting score is bigger than a threshold.  This approach is similar to prior works that use  IR~\cite{Denys:FCA12} and NL analysis~\cite{Hill:FindConcept07} for feature location. I choose IR approach because other approaches require history or structural analysis that might not be feasible for partial program. TF-IDF =  $avg( \log (1 + f_{t,d}) \times  \log \frac {N} {n_t}), f_{t,d}$ is the frequency of term $t$ in method $d$, $N$ is the total number of methods, $n_t$ is the number of methods that have the term $t$.

@@

\subsection{Example Clustering Phase.}

We take three steps in this phase. Based on the type facts extracted from partial program analysis, we first cluster similar code examples based on the number of shared class-level facts and API calls (i.e.,  \codefont{call} facts) to reduce the duplicated code snippets. Next, for each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related elements. Finally, we group auxiliary features based on program slicing and lexical similarity.

\noindent{\textbf{Cluster Examples.}}   We greedily select the most suitable structural correspondence~\cite{Cottrell:jigsaw08} and propagate the similarity of {\it object} nodes to the {\it subject} node.

@@

 Next, we try to match the fact   \codefont{(actionPerformed, calls, updateUndoState())}. Knowing that there is an edge from \codefont{updateUndoState()} to \codefont{setEnabled(undo.canUndo()} in RDF graph, we recursively match the fact \codefont{(updateUndoState, calls, setEnabled(undo.canUndo()))}  with  \codefont{(actionPerformed, calls, setEnabled(undo.canUndo()))}. The similarity score of {\it object} node \codefont{(updateUndoState, calls, setEnabled(undo.can Undo()))} is propagated to {\it subject} node \codefont{(actionPerformed, calls, updateUndoState())} as 0.4 compared to fact  \codefont{(actionPerformed, calls, setEnabled(undo. canUndo()))} in class \codefont{UndoAction}.  Our tool keeps on performing this matching until all facts in the target (Figure~\ref{fig:cluster1} (A)) is assigned a similarity score as 0 (i.e., fail to find correspondence) or a similarity score with other facts in the compared node.

Finally, the examples are clustered based on the number of  {\it object} nodes (without outer edge).  Our tool keeps on refining the large cluster to present a structured code examples to developers.

\noindent{\textbf{Extract Example Skeleton.}}  We extract all matched {\it object} nodes (without outer edge) and use them as  match seeds. We then perform dependency analysis to  extract example skeleton.  An example skeleton should start from an element without any inner edge and end at an element without any outer edge which covers all match seeds.

When selecting features, we use three rules to rank features in different examples: 1) the cost of reuse; 2) the number of resolved relationship; 3) the frequency of the feature in multiple examples; 4) the simplicity of code implementation.

The cost of reuse is measured as the number of outer edges in RDF graph, i.e., the more outer edges in RDF graph, the more expensive to reuse because it has more dependencies. We have rule 2) because  some of the relationships can not be resolved in partial program. When user tries to reuse the example, they have to manually resolve these external relationships. For instance, in Figure~\ref{fig:cluster2} (D), the feature group B.1 (\codefont{mUndoAction = new LintEditAction(undoAction, getEditorDelegate().getEditor())}) is not selected because the class \codefont{LintEditAction} cannot be resolved based on this partial program. The first two rules ease the reusability of our suggested code example. The third rule makes sure that the feature is representative and the last rule improves the understandability of our results. The simplicity is measured as the length of the code. For instance, we prefer \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants.UNDO, undo)} in Figure~\ref{fig:cluster24} (D) than \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants.UNDO, getAction((ITextEditor) part,  ITextEditorActionConstants.UNDO))} because the former one is easier to interpret.

\noindent{\textbf{Group Auxiliary Features.}}    The auxiliary features are different example  skeletons.  (TBD)

\noindent{\textbf{Enable User Interaction.}}    The user could select the features and our tool is able to extract related elements based on their selection. (TBD)

>>>>

\input{dataset_table}
\section{Approach}
Without confined to an established code corpus, we use code search engine to extract code examples based on free-form queries from users.  We build our tool in a plugin mechanism so that any code search engine can be easily planted into our system.  
We choose SearchCode~\cite{SearchCode} in our prototype because 1) it has good support for free-form queries,  2) it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, 3) it has complete API documentation.

\subsection{Example Clustering Phase}

\noindent{\textbf{Reformulate User Query.}}  Most code search engines rely on text matching to extract code examples, thus vocabulary mismatching can affect their performance~\cite{Hill:NLQueryRefine14}. We therefore refine the given query using NL approaches before querying the code search engine. 
For each queried term, we perform stemming to remove derivational affixes using Porter stemmer\cite{porter:stemmer} (e.g., parsing$\rightarrow$parse).  \textit{and identify salient terms (verbs, nouns, and adjectives) using a POS tagger~\cite{postagger04:stanford}. We choose these terms because prior work shows that they are salient elements in the query and other terms such as proposition, conjunction, and pronoun always impact query performance~\cite{Hill:NLQueryRefine14}. For example, the proposition \codefont{in} always matches the term \codefont{plugin}, leading to a false positive result). }
To achieve better search result, we leverage  WordNet to generate English synonyms (e.g., \codefont{inquire} and \codefont{query}) and software-specific word thesaurus~\cite{yangMSR12:semWord, SEWordSim:ICSE14} to identify semantically-related terms (e.g., \codefont{source} and \codefont{target}). Our  approach is similar to other \textit{automatic query refinement} approaches, which have shown up to 41\% improvement in precision and 30\% increase in recall~\cite{lopes:queryExpand14, Marcus:queryReform13}. 
Our preliminary study also shows that our query refinement approach works well to extract more related code examples. For instance, code search engine returns nothing for the query \codefont{inspect hard-drive for music files}, yet when we refine the query using  the synonym of the term \codefont{inspect}---\codefont{check}, we successfully obtain 10 related code examples.

\noindent{\textbf{Locate Queried Features.}}  Considering that source code examples are always entangled with multiple features, we separate program elements that are related to the queried features from big code examples. We do not cluster code examples based on the entire code example because it leads to too much noise in our preliminary study shown in Table~\ref{tab:preStudy}. For instance, one of the code examples for the query `\codefont{undo redo TextEditor}' contains 10 inner classes with 1447 lines of code: \codefont{CopyAction, PasteAction, MoveAction,..., UndoAction, RedoAction}, and only the last two inner classes (147 lines) are related to the queried feature.

There exist a variety of feature location approaches based on IR approach, dynamic execution trace, and historical information. We adopt a plugin mechanism and select an IR approach similar to~\cite{Marcus:LSI04}.
 We extract type names, method calls, and  identifier names, split them  into tokens using Samurai identifier splitting approach~\cite{samurai:msr09}, and convert each method into a document of Latent Semantic Index (LSI) space using an off-the-shelf tool call Semantic Vector~\cite{semanticVector:10}. \textit{Existing corpus-based feature location tools always leverage comments or even informal documents for feature location, but we only use reliable information from code elements because web-based code search engine provides us a fruitful of code examples.}
The user query is also converted to a document of LSI space.  We measure the  LSI similarity between user query and each method to identify query-related methods.  We set  a threshold for LSI similarity score to include all related methods for the given query and filter out unrelated elements. 
%I use the mean of TF-IDF weight  for each query term as a weighting factor and select all methods whose weighting score is bigger than a threshold.  This approach is similar to prior works that use  IR~\cite{Denys:FCA12} and NL analysis~\cite{Hill:FindConcept07} for feature location. I choose IR approach because other approaches require history or structural analysis that might not be feasible for partial program. TF-IDF =  $avg( \log (1 + f_{t,d}) \times  \log \frac {N} {n_t}), f_{t,d}$ is the frequency of term $t$ in method $d$, $N$ is the total number of methods, $n_t$ is the number of methods that have the term $t$.

\noindent{\textbf{Cluster Extracted Features. }}  After extracting queried features from each code examples, we automatically cluster search results using Latent Dirichlet allocation (LDA). LDA is a generative  model to express each document as a probability distribution of topics, and each topic is a probability distribution of words. Words can belong to multiple topics and documents can contain multiple topics.  We use a popular topic modeling toolkit called MALLET~\cite{McCallumMALLET} to train topic model. 
To find a near-optimal LDA configuration (the number of topic, Dirichlet prior on the per-topic word distribution, etc), we reimplement a simple Genetic-Algorithm according to~\cite{Denys:LDAGA13} for each query task. We set the maximum number of topics $k$ as 9 following Miller's law in cognitive psychology~\cite{Miller:72}. We present the generated topics to users, so that user can select the example clusters they prefer. Hindle et al. \/conducted a case study in Microsoft to investigate if the topics extracted from requirements were relevant to development feature~\cite{Hindle:topicModel12}, and their result shows that experienced developers who are familiar with features are comfortable to identify behaviors based on topic words. We hypothesize that our users can also identify expected behavior based on topic words. User can choose to view more words in a topic to help them identify which topic they prefer. As shown in Table~\ref{tab:LDA}, if user prefers to implement a  \codefont{java.swing.TextEditor} that supports undo/redo action, she may choose Topic 1 because it contains keyword \codefont{viewer, action, listener} which seems related; yet if she wants to implement a TextEditor for a Eclipse Plugin, Topic 7 is the most promising one because of the keyword \codefont{workbench, plugin}.

\begin{table}
\begin{center}
\caption{Clustering Result }
\label{tab:LDA}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{0.5\textwidth}{@{}l|l|rrr@{}} \hline
 \multicolumn{3}{c}{Query: `\codefont{undo redo TextEditor}' } \\ \hline
 Topic&Topic Words &\# E\\\hline
 1&viewer undo manager redo action listener provider& 17\\
2&selection event undo change redo builder target& 14\\
3&action factory editor undo redo constants text bars & 23\\
4&editor text menu action site group page & 18\\
5&document string outline file command set java &8\\
6&undo manager context operation element tab history &8\\
7&undo redo workbench listener shared plugin tool&6\\ \hline
 \multicolumn{3}{c}{Query: `\codefont{track mouse hover}' } \\ \hline
Topic&Topic Words &\# E\\\hline
1&mouse hover property handler  event drag data&13\\ 
2&mouse component object key select item component &11\\
3&track mouse scene parent node local client &4\\
4&mouse bound height width series listener native &11\\ \hline
\end{tabular*}
 \label{tab:dataset}
 {\# E}: the number of Examples
}
 \end{center}
\end{table}

\subsection{Example Skeleton Generation Phase}

We take three steps in this phase. For the selected code example cluster, we  first extract type facts for the located methods that belong to the queried feature.  For each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related methods as auxiliary feature. Finally, we rank the related elements and select the best-fit one to generate a reusable code example skeleton with common facts. Our tool also enables users to drag and drop other auxiliary features to generate desired code example.

@@

 \noindent{\textbf{Extract Example Skeleton.}}

 We greedily select the most suitable structural correspondence~\cite{Cottrell:jigsaw08} and propagate the similarity of {\it object} nodes to the {\it subject} node.

@@

We try to match the fact   \codefont{(actionPerformed, calls, updateUndoState())}. Knowing that there is an edge from \codefont{updateUndoState()} to \codefont{setEnabled(undo.canUndo()} in RDF graph, we recursively match the fact \codefont{(updateUndoState, calls, setEnabled(undo.canUndo()))}  with  \codefont{(actionPerformed, calls, setEnabled(undo.canUndo()))}. The similarity score of {\it object} node \codefont{(updateUndoState, calls, setEnabled(undo.can Undo()))} is propagated to {\it subject} node \codefont{(actionPerformed, calls, updateUndoState())} as 0.4 compared to fact  \codefont{(actionPerformed, calls, setEnabled(undo. canUndo()))} in class \codefont{UndoAction}.  Our tool keeps on performing this matching until all facts in the target (Figure~\ref{fig:cluster1} (A)) is assigned a similarity score as 0 (i.e., fail to find correspondence) or a similarity score with other facts in the compared node.

%Finally, the examples are clustered based on the number of  {\it object} nodes (without outer edge).  Our tool keeps on refining the large cluster to present a structured code examples to developers.

We extract all matched {\it object} nodes (without outer edge) and use them as  match seeds.

\noindent{\textbf{Rank Related Elements.}}   
 We perform dependency analysis to  extract example skeleton.  An example skeleton should start from an element without any inner edge and end at an element without any outer edge which covers all match seeds. 
When selecting features, we use three rules to rank features in different examples: 1) the cost of reuse; 2) the number of resolved relationship; 3) the frequency of the feature in multiple examples; 4) the simplicity of code implementation. 
The cost of reuse is measured as the number of outer edges in RDF graph, i.e., the more outer edges in RDF graph, the more expensive to reuse because it has more dependencies. We have rule 2) because  some of the relationships can not be resolved in partial program. When user tries to reuse the example, they have to manually resolve these external relationships.

For instance, in Figure~\ref{fig:cluster2} (D), the feature group B.1 (\codefont{mUndo Action = new LintEditAction(undoAction, getEditorDelegate().getEditor())}) is not selected because the class \codefont{LintEditAction} cannot be resolved based on this partial program. The first two rules ease the reusability of our suggested code example. The third rule makes sure that the feature is representative and the last rule improves the understandability of our results. The simplicity is measured as the length of the code. For instance, we prefer \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants .UNDO, undo)} in Figure~\ref{fig:cluster24} (D) than \codefont{actionBars.setGlobal ActionHandler (ITextEditorActionConstants.UNDO, getAction((ITextEditor) part,  ITextEditorActionConstants.UNDO))} because the former one is easier to interpret.

\noindent{\textbf{Enable User Interaction.}}  Apart from the selected best-fit related program elements, our tool also lists a fuzzy set of suggested program elements that can be added into the example skeleton. Users can drag-and-drop their preferred features to the code skeleton and our tool is able to select related program elements associated with this feature to fill in the skeleton. For instance, in Figure~\ref{fig:cluster2} (D), if user wants to add \codefont{propertyChange()} methods into the code skeleton, our tool will add super interface \codefont{PropertyChangeListener} to both \codefont{UndoAction} and \codefont{RedoAction} based on RDF graph, which are tagged as \codefont{B.4} in Figure~\ref{fig:cluster2} (D).
